\addcontentsline{toc}{chapter}{Bibliography}
\bibliographystyle{plain}
\bibliography{bibl_tesi}
\begin{thebibliography}{9}

\bibitem{mape}
Mieso Denko, Laurence Tianruo Yang, Yan Zhang.
\textit{Autonomic Computing and Networking.}
Springer Science \& Business Media, Jun 12, 2009.

\bibitem{monitor}
L. Baresi and S. Guinea.
\textit{Event-Based Multi-level
Service Monitoring.}
In Proceedings of the 20th
International Conference on Web Services, ICWS, pages 83\-90, 2013.

\bibitem{planner}
F. Seracini, M. Menarini, I. Krueger, L. Baresi,
S. Guinea, and G. Quattrocchi.
\textit{A Comprehensive
Resource Management Solution for Web-based
Systems.}
 In Proceedings of the 11th International
Conference on Autonomic Computing, ICAC - to
appear, 2014.

\bibitem{executor}
L. Baresi,
S. Guinea, and G. Quattrocchi.
\textit{Distributed Coordinated Adaptation
of Cloud-based Applications.}
Politecnico di Milano
Dipartimento di Elettronica, Informazione e Bioingegneria.

\bibitem{planner-new}
L. Baresi, S. Guinea, A. Leva, and G. Quattrocchi
\textit{A Discrete-Time Feedback Controller
for Containerized Cloud Applications}
Politecnico di Milano
Dipartimento di Elettronica, Informazione e Bioingegneria.

\bibitem{aws-autoscaling}
Amazon EC2 Autoscaling.\\
https://aws.amazon.com/autoscaling/.

\bibitem{aws-containers}
Amazon EC2 Container Service (ECS).\\
https://aws.amazon.com/ecs/.

\bibitem{docker}
Docker. \\
https://docker.com.

\bibitem{vagrant}
Vagrant.  \\
https://www.vagrantup.com.

\bibitem{cloud-computing}
M. Armbrust, A. Fox, R. Griffith, A. D. Joseph,
R. Katz, A. Konwinski, G. Lee, D. Patterson,
A. Rabkin, I. Stoica, and M. Zaharia.
\textit{A view of cloud
computing.}
Commun. ACM, 53(4):50-58, Apr. 2010.

\bibitem{self-adaptive}
H. Kienle, M. Litoiu, H. Müller, M. Pezzè, and
M. Shaw. Engineering self-adaptive systems through
feedback loops.
\textit{In Software engineering for
self-adaptive systems.}
Pages 48-70. Springer, 2009.

\bibitem{adaptation}
A. Gandhi, P. Dube, A. Karve, A. Kochut, and
L. Zhang.
\textit{Adaptive, model-driven autoscaling for
cloud applications.}
In 11th International Conference
on Autonomic Computing (ICAC 14), pages 57-64,
Philadelphia, PA, June 2014. USENIX Association.

\bibitem{asdfsadfasdfasdf}
Y. Hu, J. Wong, G. Iszlai, and M. Litoiu.
\textit{Resource
provisioning for cloud computing. In Proceedings of
the 2009 Conference of the Center for Advanced
Studies on Collaborative Research.}
Pages 101-111.
IBM Corp., 2009.

\iffalse
\bibitem{asdfasfasfasfasdfasf}
Amazonsafasdfsafasfdasdf \\
asfdsadfasfsadfsa

\bibitem{asdfsadfasdfasdf}
asdfasfasfasdfasdf
\textit{asdfasdfasdfasdf}
asdfasdfasdfasdfasdfasd

\bibitem{latexcompanion} 
Michel Goossens, Frank Mittelbach, and Alexander Samarin. 
\textit{The \LaTeX\ Companion}. 
Addison-Wesley, Reading, Massachusetts, 1993.
 
\bibitem{einstein} 
Albert Einstein. 
\textit{Zur Elektrodynamik bewegter K{\"o}rper}. (German) 
[\textit{On the electrodynamics of moving bodies}]. 
Annalen der Physik, 322(10):891 921, 1905.
 
\bibitem{knuthwebsite} 
Knuth: Computers and Typesetting,
\\\texttt{http://www-cs-faculty.stanford.edu/\~{}uno/abcde.html}
\fi


\end{thebibliography}

